\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-07 doc/paper.tex
doc/paper.tex: join a split command line
doc/paper.tex: correct a likely typo

\fs can be downloaded as a gzipped tar file from
\url{http://flexiblesusy.hepforge.org/}.  To download and install
version 1.0.0 run:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-1.0.0.tar.gz
$ tar -xf FlexibleSUSY-1.0.0.tar.gz
$ cd FlexibleSUSY-1.0.0/
\end{lstlisting}%% $
%
A CMSSM spectrum generator can be created with the following three
commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a CMSSM model file.  The \code{configure} script checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start \mathematica to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
%
\begin{lstlisting}[language=bash]
$ models/MSSM/run_MSSM.x \
    --slha-input-file=model_files/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $
%
When executed, the spectrum generator tries to find a set of \DRbar\
model parameters consistent with all CMSSM boundary conditions for the
parameter point given in the SLHA input file
\code{model_files/MSSM/LesHouches.in.MSSM}.  Afterwards, the pole mass
spectrum and mixing matrices are calculated and written to the command
line in SLHA format \cite{Skands:2003cj,Allanach:2008qq}.  For the
parameter point given in the above example the calculated pole mass
spectrum reads
%
\begin{lstlisting}
Block MASS
   1000021     1.15236966E+03   # Glu
   1000024     3.85774334E+02   # Cha_1
   1000037     6.50460073E+02   # Cha_2
        25     1.14766149E+02   # hh_1
        35     7.06792640E+02   # hh_2
        37     7.11388516E+02   # Hpm_2
        36     7.06523105E+02   # Ah_2
   1000012     3.51856376E+02   # Sv_1
   1000014     3.53042556E+02   # Sv_2
   1000016     3.53046504E+02   # Sv_3
   1000022     2.03889780E+02   # Chi_1
   1000023     3.85760714E+02   # Chi_2
   1000025     6.36544884E+02   # Chi_3
   1000035     6.50133768E+02   # Chi_4
   1000001     9.66656018E+02   # Sd_1
   1000003     1.00983181E+03   # Sd_2
   1000005     1.01651873E+03   # Sd_3
   2000001     1.01653005E+03   # Sd_4
   2000003     1.06089534E+03   # Sd_5
   2000005     1.06090238E+03   # Sd_6
   1000011     2.22570305E+02   # Se_1
   1000013     2.29864536E+02   # Se_2
   1000015     2.29888846E+02   # Se_3
   2000011     3.61946671E+02   # Se_4
   2000013     3.61950866E+02   # Se_5
   2000015     3.63136031E+02   # Se_6
   1000002     8.09787818E+02   # Su_1
   1000004     1.01454197E+03   # Su_2
   1000006     1.01981109E+03   # Su_3
   2000002     1.02015269E+03   # Su_4
   2000004     1.05807759E+03   # Su_5
   2000006     1.05808168E+03   # Su_6
\end{lstlisting}

@@

TODO: Adding tests against the CE$_6$SSM?  \cite{Athron:2009bs,Athron:2012pw}

@@

The generated code has extensively tested against Softsusy, and
additional tests have been carried out for non-minimal models, the
\ESSM and MRSSM.  Speed tests have also been performed against
Softsusy, SPheno and SPheno-like MSSM code generated by SARAH,
demonstrating that \fs runs faster than all three.

>>>>

\fs can be downloaded as a gzipped tar file from
\url{http://flexiblesusy.hepforge.org/}.  To download and install
version 1.0.0 run:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-1.0.0.tar.gz
$ tar -xf FlexibleSUSY-1.0.0.tar.gz
$ cd FlexibleSUSY-1.0.0/
\end{lstlisting}%% $
%
A CMSSM spectrum generator can be created with the following three
commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a CMSSM model file.  The \code{configure} script checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start \mathematica to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
%
\begin{lstlisting}[language=bash]
$ models/MSSM/run_MSSM.x --slha-input-file=model_files/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $
%
When executed, the spectrum generator tries to find a set of \DRbar\
model parameters consistent with all CMSSM boundary conditions for the
parameter point given in the SLHA input file
\code{model_files/MSSM/LesHouches.in.MSSM}.  Afterwards, the pole mass
spectrum and mixing matrices are calculated and written to the command
line in SLHA format \cite{Skands:2003cj,Allanach:2008qq}.  For the
parameter point given in the above example the calculated pole mass
spectrum reads
%
\begin{lstlisting}
Block MASS
   1000021     1.15236966E+03   # Glu
   1000024     3.85774334E+02   # Cha_1
   1000037     6.50460073E+02   # Cha_2
        25     1.14766149E+02   # hh_1
        35     7.06792640E+02   # hh_2
        37     7.11388516E+02   # Hpm_2
        36     7.06523105E+02   # Ah_2
   1000012     3.51856376E+02   # Sv_1
   1000014     3.53042556E+02   # Sv_2
   1000016     3.53046504E+02   # Sv_3
   1000022     2.03889780E+02   # Chi_1
   1000023     3.85760714E+02   # Chi_2
   1000025     6.36544884E+02   # Chi_3
   1000035     6.50133768E+02   # Chi_4
   1000001     9.66656018E+02   # Sd_1
   1000003     1.00983181E+03   # Sd_2
   1000005     1.01651873E+03   # Sd_3
   2000001     1.01653005E+03   # Sd_4
   2000003     1.06089534E+03   # Sd_5
   2000005     1.06090238E+03   # Sd_6
   1000011     2.22570305E+02   # Se_1
   1000013     2.29864536E+02   # Se_2
   1000015     2.29888846E+02   # Se_3
   2000011     3.61946671E+02   # Se_4
   2000013     3.61950866E+02   # Se_5
   2000015     3.63136031E+02   # Se_6
   1000002     8.09787818E+02   # Su_1
   1000004     1.01454197E+03   # Su_2
   1000006     1.01981109E+03   # Su_3
   2000002     1.02015269E+03   # Su_4
   2000004     1.05807759E+03   # Su_5
   2000006     1.05808168E+03   # Su_6
\end{lstlisting}

@@

\fs generated NUH \ESSM has also been compared against a handwritten
spectrum generator for a constrained version of the \ESSM
\cite{Athron:2009bs,Athron:2012pw}.  The RGEs could be compared
directly in unit tests and were found to match.  The handwritten code
doesn't include full one loop self energies or tadpoles so tests on
these were not carried.  Although the generators assume different
constraints they could be compared by using the output of the
CE$_6$SSM as input to \fs and the spectra were found to be in
reasonable agreement, given the different levels of precision.

@@

The generated code has been extensively tested against Softsusy, and
additional tests have been carried out for non-minimal models, the
\ESSM and MRSSM.  Speed tests have also been performed against
Softsusy, SPheno and SPheno-like MSSM code generated by SARAH,
demonstrating that \fs runs faster than all three.
